\section{Basic advance}
To change between the different ways of advancing the solution, change
the code in advance() between the godunov, molrk2 and molrk3 options.

MOLRK2 follows the same RK2 algorithm as CNS.
MOLRK3 follows the algorithm described in gottlieb, et al.
$$
u^(1) = u^n +  + \dt L(u^n)  \\
u^(2) = (3/4) u^n + (1/4) u^(1)  + (1/4) L(u^(1))
u^{n+1} = (1/3) u^n + (2/3) u^(2)  + (2/3) L(u(2))
$$

\subsection{Flux register factors}

Since 
$$
u^{n+1} = (1/3) u^n + (2/3) u^(2)  + (2/3) \dt L(u(2))
$$

This means 
$$
u^{n+1} = (1/3) u^n + (2/3)((3/4)(u^n) + (1/4)(u^1) + (1/4)\dt L(u^1))  + (2/3)( \dt L(u(2)))
$$

which, in turn, means
$$
u^{n+1} = (1/3) u^n + (2/3)((3/4)(u^n) + (1/4)(u^n + \dt L(u^n)) + (1/4)\dt L(u^1))  + (2/3)( \dt L(u^2))
$$

So the coefficient of $L(u^n) = (2/3)(1/4)\dt$, so I should set the
flux register coefficient for the first evaluation $c_n = (1/6)\dt$.
The coeffcient of $L(u^1) = (2/3)(1/4)\dt = 1/6 \dt$
The coeffcient of $L(u^2) = (2/3) \dt$.   So for the three evaluations
of the operator, the time step  that fluxes should see are $\dt/6,
dt/6, 2\dt/3$, respectively.


\section{Stuff I am not sure about}

\begin{itemize}
  \item I am not sure where to set the time levels  in the fill patch thing.
  \item I am not sure what time to use for time dependent
    vellocities.   
\end{itemize}


\section{Basic Algorithm}

We start with cell averaged scalar $<\phi>$ and a pointwise velocity at faces.

\begin{itemize}
  \item Get pointwise $\phi$ because I will need this to get higher
    order gradient at faces.  
$$
\phi = <\phi> -\frac{h^2}{24}(L(<\phi>)),
$$
   where $L$ is the standard second order Laplacian.
\item Get the average of the scalar over the faces .
$$
<\phi>_{i+1/2} =  \frac{7}{12}(<\phi>_i    + <\phi>_{i+1})
                -\frac{1}{12}(<\phi>_{i-1} + <\phi>_{i+2})
$$

\item Get the point values of the scalar on faces from the face
  average:
$$
\phi_{i+1/2} = <\phi>_{i+1/2} - \frac{1}{24} L^T(<phi>)_{i+1/2},
$$
where $L^T$ is the Laplacian that does not include terms normal to the
face (what McCorquodale refers to as the ``transverse Laplacian'').

\item Compute pointwise fluxes $F$ (including diffusion fluxes).
$$
F_{i+1/2} = u_{i+1/2} \phi_{i+1/2}  - nu G^x(phi)_{i+1/2}
$$
where the normal gradient $G^x$ is computed using fourth order finite
differences  of the pointwise cell-centered scalar $\phi$.
$$
G^x(\phi)_{i+1/2} = \frac{\partial \phi}{\partial x} + O(h^4) 
= (1/h)(\phi_{i+1}-\phi_{i}) 
- (1/(4h))((\phi_{i+2} + \phi_i - 2\phi_{i+1}) - (\phi_{i+1} + \phi_{i-1} - 2\phi_{i}))
$$

\item Transform the pointwise fluxes $F$ into face-averaged fluxes $<F>$
$$
<F> = F - (1/24) L^T(F).
$$    
\end{itemize}
